---
output: github_document
bibliography: reference.bib  
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Replication: "Simultaneous Inference Bands for Autocorrelations"

This repository contains replication files for the paper "Simultaneous Inference Bands for Autocorrelations" by Uwe Hassler, Marc-Oliver Pohle and Tanja Zahn. The `R` package accompanying the paper is available under the repository [ACFbands](https://github.com/TanjaZahn/ACFbands).

## Installation and Downloading Data

Before running the replication code, the accompanying `R` package [ACFbands](https://github.com/TanjaZahn/ACFbands) has to be installed from Github:

```{r, results = FALSE,  message=FALSE, eval = FALSE}
install.packages("devtools")
library(devtools)
install_github("TanjaZahn/ACFbands")
```

To install the other packages used in the replication files, run the code:

```{r, results = FALSE,  message=FALSE, eval = FALSE}
install.packages("tidyverse")
install.packages("lubridate")
install.packages("patchwork")
install.packages("stargazer")
install.packages("xtable")
install.packages("kableExtra")

```

The data used in the empirical application has been downloaded from the [FRED-MD database](https://www.stlouisfed.org/research/economists/mccracken/fred-databases), see also the [working paper](https://s3.amazonaws.com/real.stlouisfed.org/wp/2015/2015-012.pdf) by @mccracken2016 for a description. To replicate results, please download the `2024-07.csv` data set from the website or by clicking this [link](https://www.stlouisfed.org/-/media/project/frbstl/stlouisfed/research/fred-md/monthly/2024-07.csv?sc_lang=en&hash=876A1CCE26C20876594956013802F191=) (download will start immediately). After downloading, please save the file under the name “FRED-MD-2024-07” in the subfolder called "data".


## code

The folder "code" includes the `R` code that was used to create all the results in the paper. It contains several subfolders. Within the subfolder, `R` scripts are numerated in the respective order. We give a short overview:

* **analytical_examples:** contains the files that are used to show the properties of the inference bands for the example of an AR(1) process (Figures 3 to 7 as well as the examples for the B matrices contained in the Appendix).

* **application:** contains the files used in the empirical application in section 7 and Appendix E.

* **sim_ts:** produces the simulation results for time series, i.e. sections 6.1 and 6.2.

* **sim_dyn:** produces the simulation results for dynamic regressions, i.e. section 6.3.

* **functions:** contains some custom functions that files from the other folders use. They will be called upon automatically in the respective places. Thus, the files contained in "functions" do not have to be run explicitly.

* **mytheme:** contains some graphical settings for the plots. This file does not have to be run explicitly.

*Note*: Most of the code in **sim_ts** and **sim_dyn** checks if simulation results are already available in the folder **results** and is only executed, if they are not. 


## data

After downloading the data set from [FRED-MD](https://www.stlouisfed.org/research/economists/mccracken/fred-databases), please store it in this folder, see the remark under "Installation and Downloading Data".

## results

The raw results from the simulation runs are stored in the folder "results" for the time series case ("sim_ts") and for dynamic regression residuals ("sim_ts").

## graphics

This folder contains all plots and tables.

## References





