---
output: github_document
bibliography: reference.bib  
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Replication: "Simultaneous Inference Bands for Autocorrelations"

This repository contains replication files for the paper ["Simultaneous Inference Bands for Autocorrelations"](https://arxiv.org/abs/2503.18560) by Uwe Hassler, Marc-Oliver Pohle and Tanja Zahn. The `R` package accompanying the paper is available under the repository [ACFbands](https://github.com/TanjaZahn/ACFbands).

## Installation and Downloading Data

Before running the replication code, the accompanying `R` package [ACFbands](https://github.com/TanjaZahn/ACFbands) has to be installed from Github:

```{r, results = FALSE,  message=FALSE, eval = FALSE}
# install.packages("devtools")
library(devtools)
pak::pak("TanjaZahn/ACFbands")
library(ACFbands)
```

To install the other packages used in the replication files, run the code:

```{r, results = FALSE,  message=FALSE, eval = FALSE}
install.packages("tidyverse")
install.packages("lubridate")
install.packages("patchwork")
install.packages("stargazer")
install.packages("xtable")
install.packages("kableExtra")
install.packages("testcorr")

```

The data used in the macroeconomic case study has been downloaded from the [FRED-MD database](https://www.stlouisfed.org/research/economists/mccracken/fred-databases), see also the [working paper](https://s3.amazonaws.com/real.stlouisfed.org/wp/2015/2015-012.pdf) by @mccracken2016 for a description. To replicate results, please download the `2024-07.csv` data set from the website or by clicking this [link](https://www.stlouisfed.org/-/media/project/frbstl/stlouisfed/research/fred-md/monthly/2024-07.csv?sc_lang=en&hash=876A1CCE26C20876594956013802F191=) (download will start immediately). After downloading, please save the file under the name “FRED-MD-2024-07.csv” in the subfolder called "data".

Daily Fama-French data (three factors) excess returns have been downloaded from the [Fama-French data library](https://mba.tuck.dartmouth.edu/pages/faculty/ken.french/data_
library.html), see also @fama2023. To replicate results, please download the data set from the website and save the file under the name “fama_french_daily.txt" in the subfolder called "data".  


## code

The folder "code" includes the `R` code that was used to create all the results in the paper. It contains several subfolders. Within the subfolder, `R` scripts are numerated in the respective order. We give a short overview:

* **analytical_examples:** contains the files that are used to show the properties of the inference bands for the theoretical example of an AR(1) process.

* **application:** contains the files used in the case studies.

* **functions:** contains some custom functions that files from the other folders use. They will be called upon automatically in the respective places. Thus, the files contained in "functions" do not have to be run explicitly.

* **sim_dyn:** produces the simulation results for dynamic regressions with iid errors.

* **sim_dyn_garch:** produces the simulation results for dynamic regressions with normal GARCH errors.

* **sim_ts:** produces the simulation results for time series with iid errors.

* **sim_ts_garch:** produces the simulation results for time series with normal GARCH errors.

* **sim_ts_garch_chi2:** produces the simulation results for time series with Chi-square GARCH errors.

* **mytheme:** contains some graphical settings for the plots. This file does not have to be run explicitly.

*Note*: Most of the code to reproduce simulation results checks if results are already available in the folder **results** and is only executed, if they are not. 


## data

After downloading the data sets, please store it in this folder, see the remark under "Installation and Downloading Data".

## results

The raw results from the simulation runs are stored in the folder "results" using the same names for the subfolders as above (see "code").

## graphics

This folder contains all plots and tables.

## References





